\thetitle

### 2021-05-26 writing/discussion.tex
revision of general threats discussiom

The validity of these conclusions is threatened in two fundamentally distinct
ways. The first sets of threats have been mentioned before: (i) the
representativeness of benchmarks; (ii) the relation between mutations and real
programming mistakes; and (iii) the sampling strategy.  While the experimental setup attempts to
mitigate against these threats, the reader must definitely take into account
these limitations of the experiment and must understand that the collected data
not support any further generalization.

The second set of threats connects the experiment with reality or, more
precisely, assess how close the connection is. To start with, it questions the
realism of the rational programmer itself (sec.~\ref{sub:rational}), followed by
the definition of ``interesting scenarios''
(sec.~\ref{sec:threat:erasure-bias}).  The remaining questions address the
accuracy and the cost of Transient blame, respectively (see
secs.~\ref{sec:threat:transient} and~\ref{sec:threat:transient2}).

>>>>

The validity of these conclusions is threatened in two distinct
ways. The first set of threats concerns easy-to-tune parameters of the
experiment and have been mentioned before: (i) the
representativeness of benchmarks; (ii) the relation between the mutations and real
programming mistakes; and (iii) the sampling strategy.  While the experimental setup attempts to
mitigate against these threats, the reader must definitely take into account
these limitations of the experiment when generalizing its conclusions.

The second set of threats connects the fundamental ideas and infrastructure of the experiment with reality or, more
precisely, assess how close the connection is. To start with, it questions the
realism of the rational programmer itself (sec.~\ref{sub:rational}), followed by
the definition of ``interesting scenarios''
(sec.~\ref{sec:threat:erasure-bias}).  The remaining questions address the
accuracy and the cost of Transient blame, respectively (see
secs.~\ref{sec:threat:transient} and~\ref{sec:threat:transient2}).
